Windowed Developer Topic Analysis

### 2009-03-16 lda-paper.tex
more changes

Topic analysis, with respect to Software Control Systems (SCSs), is
valuable as it has many uses for the stakeholders involved.

Example scenarios where the usage of this technique would prove useful
are numerous. Imagine a development team has agreed to implement some
features at the start of an iteration. By the end of the iteration
only some of the agreed upon features are implemented. The developers
swear they were focusing solely on the features agreed upon. Topic
analysis could help by teasing out the distinct topics or focusses of
the developers. Perhaps the developers had to deal with issues
orthogonal to the features they were working on, but were probably
necessary to complete such features. Developers might have grouped
those orthogonal changes into one of the features and might not

@@

%3. [ ] Previous Work [0/2]
%   2. [ ] LDA Work [0/6]
\section{Results}
%   1. Interesting smears 
%   2.   postgresql
\subsection{Postgresql}
%   3.   mysql
\subsection{Mysql}
%   4.   firebird
\subsection{Firebird}
%   5.   what's that other db?
\subsection{ what's that other db?}
%7.   Validation [0/1]
\subsection{Validation}
%   1. well i'm stumped
%   2. look at it?
%   3. investigate those revisions and check the proportion etc
%   4. exploratory
%   5.   work it out
%8.   Validity Threats [0/5]
\section{Validity Threats}
%   1.   validation
%   2.   LDA is questionable
%   3.   blackbox problem
%   4.   not in the token
%   5.   multiple X token
%9.    Future Work
\section{ Future Work}
%10.   Conclusions
\section{Conclusions}
%11.   Start file file:/home/abez/projects/lda-paper/lda-paper.tex

>>>>

Topic analysis, with respect to Software Control Systems (SCSs), is
valuable as it has many uses for the stakeholders involved.  Example
scenarios where the usage of these techniques would prove useful are
numerous. Imagine a development team has agreed to implement some
features at the start of an iteration. By the end of the iteration
only some of the agreed upon features are implemented. The developers
swear they were focusing solely on the features agreed upon. Topic
analysis could help by teasing out the distinct topics or focusses of
the developers. Perhaps the developers had to deal with issues
orthogonal to the features they were working on, but were probably
necessary to complete such features. Developers might have grouped
those orthogonal changes into one of the features they were working
on, thus when asked about how their time was spent the orthogonal
changes would not be covered. This is what we hope that windowed topic
analysis can uncover. If windowed topic analysis can discover
important but overlooked topics, it can help both developers and
managers.

@@

%3. [ ] Previous Work [0/2]
%   2. [ ] LDA Work [0/6]
\section{Results}
%   1. Interesting smears 
%   2.   postgresql
\subsection{Postgresql}
%   3.   mysql
\subsection{Mysql}
%   4.   firebird
\subsection{Firebird}
%   5.   what's that other db?
\subsection{ what's that other db?}
%7.   Validation [0/1]
\subsection{Validation}
%   1. well i'm stumped
%   2. look at it?
%   3. investigate those revisions and check the proportion etc
%   4. exploratory
%   5.   work it out
%8.   Validity Threats [0/5]
\section{Validity Threats}

In this study we are explicitly trusting that the programmers annotate
their changes with relevant information. We rely on the descriptions
they provide. If the language of checkin comments was automated

%   1.   validation
%   2.   LDA is questionable
%   3.   blackbox problem
%   4.   not in the token
%   5.   multiple X token
%9.    Future Work
\section{ Future Work}
%10.   Conclusions
\section{Conclusions}
%11.   Start file file:/home/abez/projects/lda-paper/lda-paper.tex
